Reasoning About a Machine with Local Capabilities

### 2019-03-06 toplas/paper.tex
[TOPLAS] Add keywords to ML awkward example

\begin{wrapfigure}{R}{.35\textwidth}
  \centering
  \begin{tabular}{c} % see https://tex.stackexchange.com/questions/5818/how-to-center-a-listing
  \begin{lstlisting}[gobble=2,escapeinside=||]
  fun _ => 
  |\color{gray}{g1:}| let x = ref 0 in
      fun adv =>
  |\color{gray}{f4:}|   x := 0;
        adv();
        x := 1;
        adv();
        assert(x == 1)
  \end{lstlisting}
  \end{tabular}
  \caption{The original awkward example from \citet{pitts_operational_1998,Dreyer:jfp12}, in ML notation.}
  \label{fig:awkward}
\end{wrapfigure}

Let us first look at this ML program.
At the top-level, it is a lambda function that can be invoked by the context.
When it is invoked, it allocates a fresh mutable variable $x$ of integer type, initially containing the value $0$.
Next, the function returns a second closure (let's call this $\textit{cl}_x$) that can be invoked by the context whenever it chooses.
$\textit{cl}_x$ itself takes a callback function \texttt{adv} that it will invoke twice, after setting $x$ to $0$ and $1$ respectively.
After the second invocation of \texttt{adv}, $\textit{cl}_x$ will verify that $x$ is still set to $1$.

>>>>

\begin{wrapfigure}{R}{.35\textwidth}
  \centering
  \begin{tabular}{c} % see https://tex.stackexchange.com/questions/5818/how-to-center-a-listing
  \begin{lstlisting}[gobble=2,escapeinside=||,keywords={fun, let, in, ref, assert}]
  fun _ => 
  |\color{gray}{g1:}| let x = ref 0 in
      fun adv =>
  |\color{gray}{f4:}|   x := 0;
        adv();
        x := 1;
        adv();
        assert(x == 1)
  \end{lstlisting}
  \end{tabular}
  \caption{The original awkward example from \citet{pitts_operational_1998,Dreyer:jfp12}, in ML notation.}
  \label{fig:awkward}
\end{wrapfigure}

Let us first look at this ML program.
At the top-level, it is a lambda function that can be invoked by the context.
When it is invoked, it allocates a fresh mutable variable $x$ of integer type, initially containing the value $0$.
Next, the function returns a second closure (let's call this $\textit{cl}_x$) that can be invoked by the context whenever it chooses.
$\textit{cl}_x$ itself takes a callback function \texttt{adv} that it will invoke twice after setting $x$ to $0$ and $1$ respectively.
After the second invocation of \texttt{adv}, $\textit{cl}_x$ will verify that $x$ is still set to $1$.
